Generating Images from Captions\\ with Attention

### 2015-11-05 iclr-paper-new.tex
new changes

\title{Generating Images From Captions\\ With Attention}

@@

As for the quantitative comparison of different models, we first compare the performances of the model trained with variational methods. We rank the images in the test set conditioned on the captions based on the variational lower bound of the log-probabilities 
and then report the Precision-Recall metric as an evaluation of the quality of the generative model (see Table~\ref{tab:results}.). Perhaps unsurprisingly, generative models did not perform well on the image retrieval task. To deal with the large computational complexity involved in looping through each test image, we create a shortlist of one hundred images including the correct one, based on the images having the closest 
Euclidean distance in the top convolutional feature-space of a VGG-like model~\citep{simonyan_convnet} trained on the CIFAR dataset\footnote{The architecture of the model is described here \url{http://torch.ch/blog/2015/07/30/cifar.html}. The shortlist of test images used for evaluation can be downloaded from \url{http://www.cs.toronto.edu/~emansim/cap2im/test-nns.pkl}.} \citep{krizhevsky_cifar}. 
Since there are ``easy'' images for which the model assigns high log-probabilities independent of the query caption, 
we instead look at the ratio of 
the likelihood of the image conditioned on the sentence to the likelihood of the image conditioned on the mean sentence representation in the training set, following the retrieval protocol of~\citep{kiros_captions}.
We also found that the lower bound on the test log-probabilities decreased for sharpened images, and that sharpening considerably hurt the retrieval results. Since sharpening changes the statistics of images, the estimated log-probailities of image pixels is not necessarily a good metric.

>>>>

\title{Generating Images from Captions\\ with Attention}

@@

As for the quantitative comparison of different models, we first compare the performances of the model trained with variational methods. We rank the images in the test set conditioned on the captions based on the variational lower bound of the log-probabilities 
and then report the Precision-Recall metric as an evaluation of the quality of the generative model (see Table~\ref{tab:results}.). Perhaps unsurprisingly, generative models did not perform well on the image retrieval task. To deal with the large computational complexity involved in looping through each test image, we create a shortlist of one hundred images including the correct one, based on the images having the closest 
Euclidean distance in the last fully-connected feature space of a VGG-like model~\citep{simonyan_convnet} trained on the CIFAR dataset\footnote{The architecture of the model is described here \url{http://torch.ch/blog/2015/07/30/cifar.html}. The shortlist of test images used for evaluation can be downloaded from \url{http://www.cs.toronto.edu/~emansim/cap2im/test-nns.pkl}.} \citep{krizhevsky_cifar}. 
Since there are ``easy'' images for which the model assigns high log-probabilities independent of the query caption, 
we instead look at the ratio of 
the likelihood of the image conditioned on the sentence to the likelihood of the image conditioned on the mean sentence representation in the training set, following the retrieval protocol of~\citep{kiros_captions}.
We also found that the lower bound on the test log-probabilities decreased for sharpened images, and that sharpening considerably hurt the retrieval results. Since sharpening changes the statistics of images, the estimated log-probailities of image pixels is not necessarily a good metric.

### 2015-11-05 supp.tex
readded data augmentation description
new changes

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. 
The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. 
For the Microsoft COCO task, we trained our model for $18$ epochs. The learning rate was 
reduced to $0.0001$ after $11$ epochs.
\FIXME{For the MNIST with Captions task, the model was trained for ??? epochs and the 
learnign rate was reduced to ?? after ?? epochs}.   
The norm of the gradients was clipped at $10$ during training 
to avoid the exploding gradients problem.

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c c c}
\hline
\hline
 & & \multicolumn{3}{c}{\textbf{alignDRAW Model}}  & &  \\
\hline
Task & \#glimpses & Inference  & Generative  & Latent & Read Size & Write Size\\
     & \ T & Dim of $h^{infer}$ & Dim of $h^{gen}$  & Dim of $Z$  & $p$ & $p$\\
\hline
MS COCO & 32 & 550 & 550 & 275 & 9 & 9\\
MNIST   & 32 & 300 & 300 & 150 & 8 & 8\\
\end{tabulary}
\caption{The architectural configurations of alignDRAW models.}
\label{tab:drawhyper}
\end{center}
%\vspace{-0.3cm}
\end{table}

>>>>

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. 
The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. 
For the Microsoft COCO task, we trained our model for $18$ epochs. The learning rate was 
reduced to $0.0001$ after $11$ epochs.
For the MNIST with Captions task, the model was trained for 150 epochs and the 
learning rate was reduced to $0.0001$ after 110 epochs. During each epoch, randomly created $10000$ training samples were used for training.
The norm of the gradients was clipped at $10$ during training 
to avoid the exploding gradients problem.

@@

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c c c}
\hline
%\hline
 & & \multicolumn{3}{c}{\textbf{alignDRAW Model}}  & &  \\
\hline
Task & \#glimpses & Inference  & Generative  & Latent & Read Size & Write Size\\
     & \ T & Dim of $h^{infer}$ & Dim of $h^{gen}$  & Dim of $Z$  & $p$ & $p$\\
\hline
MS COCO & 32 & 550 & 550 & 275 & 9 & 9\\
MNIST   & 32 & 300 & 300 & 150 & 8 & 8\\
\end{tabulary}
\caption{The architectural configurations of alignDRAW models.}
\label{tab:drawhyper}
\end{center}
%\vspace{-0.3cm}
\end{table}
